Pangenome graph layout by Path-Guided Stochastic Gradient Descent

### 2023-09-22 manuscript/main.tex
small stuff

	Here, we present a new pangenome graph layout algorithm which applies a path-guided stochastic gradient descent (PG-SGD) to move pairs of nodes in parallel with a modified HOGWILD! strategy.
	The algorithm computes the pangenome graph layout that best reflects the nucleotide sequences in the graph.
	To our knowledge, no algorithm takes into account such biological information to compute the graph layouts.
	PG-SGD can be extended in any number of dimensions.
	In the ODGI toolkit \citep{Guarracino2022}, we provide implementations for 1-dimensional (1D) and 2-dimensional (2D) layouts. The respective algorithms were already successfully applied to build and visualize large scale pangenome graphs of the Human Pangenome Reference Consortium (HPRC)~\citep{Liao2023, Guarracino2023}.

>>>>

	Here, we present a new pangenome graph layout algorithm which applies a path-guided stochastic gradient descent (PG-SGD) to move pairs of nodes in parallel with a modified HOGWILD! strategy.
	The algorithm computes the pangenome graph layout that best reflects the nucleotide sequences in the graph.
	To our knowledge, no algorithm takes into account such biological information to compute the graph layouts.
	PG-SGD can be extended in any number of dimensions.
	In the ODGI toolkit \citep{Guarracino2022}, we provide implementations for 1-dimensional (1D) and 2-dimensional (2D) layouts.
	These algorithms have already been successfully applied to construct and visualize large-scale pangenome graphs of the Human Pangenome Reference Consortium (HPRC)~\citep{Liao2023, Guarracino2023}.
